Papers

### 2023-09-23 quarto/index.qmd
update

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Scientist from University of Illinois Urbana-Champaign.

@@

* **A. Zhang**, Z. C. Lipton, M. Li, and A. J. Smola<br>
 	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
	*Cambridge University Press*, 2023<br>
	* Adopted at 500 universities from 70 countries
	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

>>>>

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.

@@

* **A. Zhang**, Z. C. Lipton, M. Li, and A. J. Smola<br>
 	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
	*Cambridge University Press*, 2023<br>
	* Adopted at 500 universities from 70 countries (on <a href="https://www.amazon.com/Dive-into-Learning-Aston-Zhang/dp/1009389432" target="_blank">Amazon</a>)
	* Featured in the <a href="https://youtu.be/ue9aumC7AAk?t=6856" target="_blank">AWS re:Invent keynote</a> by Swami, Head of AWS AI, Database, and Analytics<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>
